Model Finding for (Co)recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-05 tex/main.tex
mild edits -- revert anything you don't like

\newcommand{\cvc}{\textsc{cvc}{\small 4}\xspace}
\newcommand{\cvciii}{\textsc{cvc}{\small 3}\xspace}
\newcommand{\ziii}{\textsc{z}{\small 3}\xspace}
\newcommand{\teq}{\approx}
\newcommand{\cc}[1]{#1^*}
\newcommand{\terms}{\mathbf{T}}
%\newcommand{\functerms}{\mathbf{DFT}}
\newcommand{\vars}{\mathbf{V}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\J}{\mathcal{J}}
\def\AIF{\qtab\keyword{if}\ }
\def\THEN{\ \keyword{then}\ }
\def\AELSE{\untab\qtab\keyword{else}\ }
\def\FI{\untab}
\def\RETURN{\keyword{return}\ }
\def\ENDPROC{\untab}
\newcommand{\conv}{\mathcal{W}}

\newcommand{\ssorts}[1]{#1^\mathrm{s}}
\newcommand{\sfuns}[1]{#1^\mathrm{f}}
\newcommand{\sfundefs}[1]{#1^\mathrm{df}}
\newcommand{\sfunndefs}[1]{#1^\mathrm{nf}}
\newcommand{\sortint}{\mathrm{Int}}

@@

%%% I added (Co) -- hope you like it --JB
\title{Model Finding for (Co)recursive Functions in SMT\thanks{
This research is partially supported by the Inria technological development
action \relax{Contrexemples Utilisables par Isabelle et Coq} (CUIC).
}
}

@@

A \emph{signature} $\Sigma$ consists of 
a set $\ssorts{\Sigma}$ of type symbols and
a set $\sfuns{\Sigma}$ of function symbols.
We assume that signatures always include a Boolean type $\Bool$ and constants 
$\ltrue$ and $\lfalse$ of that type (respectively, for true and false), 
an (infix) equality predicate $\teq$ of type $\tau \times \tau$ for each $\tau \in \ssorts{\Sigma}$,
and standard boolean connectives ($\neg$, $\wedge$, $\vee$, etc.).
and a function $\lite$ of type $\Bool \times \tau \times \tau \rightarrow \tau$ for each $\tau \in \ssorts{\Sigma}$.
We will write $t\typ{\tau}$ to denote a term $t$ of type~$\tau$.
We write $\terms( t )$ to denote the set of subterms in $t$.
%We write $\functerms^\Sigma( t )$ to denote the set of $f$-applications in $t$ such that $f \in \sfundefs{\Sigma}$.

>>>>

\let\oldSigma=\Sigma
\def\Sigma{\mathrm{\oldSigma}}

\newcommand{\cvc}{\textsc{cvc}{\small 4}\xspace}
\newcommand{\cvciii}{\textsc{cvc}{\small 3}\xspace}
\newcommand{\ziii}{\textsc{z}{\small 3}\xspace}
\newcommand{\teq}{\approx}
\newcommand{\cc}[1]{#1^*}

%%% I'm trying to avoid bold whenever it can be avoided (except for headings
%%% etc.) --JB
%\newcommand{\terms}{\mathbf{T}}
\newcommand{\terms}{\mathcal{T}}

%\newcommand{\functerms}{\mathbf{DFT}}
\newcommand{\vars}{\mathbf{V}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\I}{\mathcal{J}} %%% there's no difference, right? --JB
\newcommand{\J}{\mathcal{J}}
\def\AIF{\qtab\keyword{if}\ }
\def\THEN{\ \keyword{then}\ }
\def\AELSE{\untab\qtab\keyword{else}\ }
\def\FI{\untab}
\def\RETURN{\keyword{return}\ }
\def\ENDPROC{\untab}
\newcommand{\conv}{\mathcal{W}}

%\newcommand{\ssorts}[1]{#1^\mathrm{s}}
\newcommand{\ssorts}[1]{#1^\mathrm{y}}

\newcommand{\sfuns}[1]{#1^\mathrm{f}}
\newcommand{\sfundefs}[1]{#1^\mathrm{df}}
\newcommand{\sfunndefs}[1]{#1^\mathrm{nf}}
\newcommand{\sortint}{\mathrm{Int}}

@@

%%% I added (Co) -- hope you like it --JB
\title{Model Finding for (Co)recursive Functions in SMT\thanks{%
This research is partially supported by the Inria technological development
action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC).
}
}

@@

A \emph{signature} $\Sigma$ consists of 
a set $\ssorts{\Sigma}$ of type symbols (sorts) and
a set $\sfuns{\Sigma}$ of function symbols.
We assume that signatures always include a Boolean type $\Bool$ and constants 
$\ltrue$ (truth) and $\lfalse$ (falsity) of that type,
an infix equality predicate $\teq$ of type $\tau \times \tau \to \Bool$
for each $\tau \in \ssorts{\Sigma}$,
standard boolean connectives ($\neg$, $\wedge$, $\vee$, etc.),
and a function $\lite$ of type $\Bool \times \tau \times \tau \rightarrow \tau$ for each $\tau \in \ssorts{\Sigma}$.
We write $t\typ{\tau}$ to denote a term $t$ of type~$\tau$.
We write $\terms( t )$ to denote the set of subterms in $t$.
%We write $\functerms^\Sigma( t )$ to denote the set of $f$-applications in $t$ such that $f \in \sfundefs{\Sigma}$.
